---
title: "Romero_Activity1"
author: "Fernando Romero"
date: "9/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Main Research Interest
***
I am interested in _**Data Science Applied to Transport Sector**_, _**Intelligent Transportation Systems**_, _**Urbanism**_ and _**Travel Behavior**_. Recent work includes studies on the impact of real-time information on route choice and how measures aimed at tackling high pollution episodes change commuter's behavior. Currently, I try to find out which transport demand management measures would foster a more sustainable mobility in a case study in Madrid. These measures include incentives for carpooling, improvements in bus travel time, or removing transfers at subway network.  
   
# Favorites
***
## Favorite Music
1. Io Vivrò Senza Te - Mina 
2. La Casa Azul - Marco Mengoni
3. Un Hombre De Verdad - Alaska  
4. I Was Born To Love You - Queen  
5. Mourir Sur Scène - Dalida

## Favorite Equation
Multinomial logit choice   

$P_{ni}=\frac{exp(B_{i}s_{n})}{\sum_{j=1}^J exp(B_{j}s_{n})}$

## Favorite Artists
Name | Achievements
:-|:-
Alfred Hitchcock | The Master of Suspense. He directed over **50 films**, the most famous are *Vertigo*, *North by Northwest* and *Psycho*.
Bette Davis | **Two** Academy Awards for Best Actress.She was the first person to garner **ten** acting Academy Award nominations.
Freddie Mercury | One of the most charismatic singers and songwriters of the 20th Century.
Mina | Italian singer who has scored **79 albums and 71 singles** on the Italian charts.
Tom Ford | In addition to be one of the most recognized fashion desginers, Tom Ford has directed two films (*A Single Man*, *Nocturnal Animals*) full of emotions and beauty that were acclaimed by film critics and at film festivals.

# A Chunk Of Code
***
Temperature in Summer 2016.  
We show the distribution of temperatures in Summer 2016, in Madrid based on daily records.
```{r echo=FALSE, warnings=FALSE, message=FALSE}
library("lubridate")
library("ggplot2")
library("tidyverse")
Date<-seq(ymd("2016-06-01",tz="Europe/Madrid"), ymd("2016-09-30",tz="Europe/Madrid"), by="day")
Temperature<-rnorm(length(Date),mean=35,sd=3)
Summer_Temp<-data.frame(Date,Temperature)
Summer_Temp %>% group_by(Month=month(Date)) %>% summarise(Average_Temperature=mean(Temperature),Deviation_Temperature=sd(Temperature))
ggplot(Summer_Temp,aes(x=Date,y=Temperature,color=Temperature))+geom_line()+geom_point()+scale_color_gradient(low="yellow",high="red")+labs(y="Temperature °C",title="Temperature in Summer 2016")

```